\begin{thebibliography}{9}
   \bibitem{nbt}  Nikola Mrk\v{s}i\'c, Diarmuid \'O S\'eaghdha, Tsung-Hsien Wen, Blaise Thomson, and Steve Young.  Neural belief tracker:  Data-driven dialogue state tracking. \textit{arXiv preprint arXiv:1606.03777}, 2016.

  \bibitem{e2e} Bing Liu and Ian Lane. An end-to-end trainable neural network model with belief tracking for task-oriented dialog. \textit{arXiv preprint arXiv:1708.05956}, 2017.

  \bibitem{dstc8} Seokhwan Kim, Michel Galley, Chulaka Gunasekara, Sungjin Lee, Adam Atkinson, Baolin Peng, Hannes Schulz, Jianfeng Gao, Jinchao Li, Mahmoud Adada, Minlie Huang, Luis Lastras, Jonathan K. Kummerfeld, Walter S. Lasecki, Chiori Hori, Anoop Cherian, Tim K. Marks, Abhinav Rastogi, Xiaoxue Zang, Srinivas Sunkara, Raghav Gupta. The Eighth Dialog System Technology Challenge. \textit{arXiv preprint arXiv:1911.06394}, 2019.

  \bibitem{letsgo} Antoine Raux, Brian Langner, Dan Bohus, Alan W Black, Maxine Eskenazi. Let's Go Public! Taking a spoken dialog system to the real world. In \textit{Proc. of InterSpeech}, pages 885-888, 2005.

  \bibitem{crf} Christian Raymond, Giuseppe Riccardi. Generative and discriminative algorithms for spoken language understanding. In \textit{Proceedings of INTERSPEECH 2007}, pages 1605-1608, 2007.

  \bibitem{pomdp} Steve Young. Using POMDPS for dialog management. In \textit{2006 IEEE Spoken Language Technology Workshop}, pages 8-13, 2006.

  \bibitem{joint}  Abhinav Rastogi, Raghav Gupta, and Dilek Hakkani-Tur. Multi-task learning for joint language understanding and dialogue state tracking. In \textit{Proceedings of the 19th Annual SIGdial Meeting on Discourse and Dialogue}, pages 376-384, 2018.

  \bibitem{bert} Jacob Devlin, Ming-Wei Chang, Kenton Lee, Kristina Toutanova. BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding. \textit{arXiv preprint arXiv:1810.04805}, 2018.

  \bibitem{transformer} Ashish Vaswani, Noam Shazeer, Niki Parmar, Jakob Uszkoreit, Llion Jones, Aidan N. Gomez, Lukasz Kaiser, Illia Polosukhin. Attention Is All You Need. \textit{arXiv preprint arXiv:1706.03762}, 2017.

  \bibitem{bert_dst} Guan-Lin Chao, Ian Lane. BERT-DST: Scalable End-to-End Dialogue State Tracking with Bidirectional Encoder Representations from Transformer. In \textit{Proceedings of INTERSPEECH 2019}, pages 1468-1472, 2019.
  
  \bibitem{kanren} Sanuj Sharma, Prafulla Kumar Choubey, and Ruihong Huang. Improving Dialogue State Tracking by Discerning the Relevant Context. In \textit{Proceedings of the 2019 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies, Volume 1 (Long and Short Papers)}, pages 576-581, 2019.

  \bibitem{glad} Victor Zhong, Caiming Xiong, Richard Socher. Global-Locally Self-Attentive Encoder for Dialogue State Tracking. In \textit{Proceedings of the 56th Annual Meeting of the Association for Computational Linguistics (Volume 1: Long Papers)}, pages 1458-1467, 2018.

  \bibitem{adam} Diederik P. Kingma and Jimmy Ba. Adam: A method for stochastic optimization. \textit{CoRR}, abs/1412.6980, 2014.

  \bibitem{multi-woz} Pawe\l \ Budzianowski, Tsung-Hsien Wen, Bo-Hsiang Tseng, I\~nigo Casanueva, Stefan Ultes, Osman Ramadan, Milica Ga\v{s}i\'c. MultiWOZ - A Large-Scale Multi-Domain Wizard-of-Oz Dataset for Task-Oriented Dialogue Modelling. \textit{arXiv preprint arXiv:1810.00278}, 2018.

  \bibitem{dstc2} Matthew Henderson, Blaise Thomson, Jason Williams. The Second Dialog State Tracking Challenge. In \textit{Proceedings of the 15th Annual Meeting of the Special Interest Group on Discourse and Dialogue (SIGDIAL)}, pages 263-272, 2014.

  \bibitem{dstc8-great} Yue Ma, Zengfeng Zeng, Dawei Zhu, Xuan LiYiying Yang, Xiaoyuan Yao, Kaijie Zhou, Jianping Shen. An End-to-End Dialogue State Tracking System withMachine Reading Comprehension and Wide \& Deep Classification. \textit{arXiv preprint arXiv:1912.09297}, 2019.
\end{thebibliography}
